---
title: "Problem 2 Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: journal
---

```{r setup, include=FALSE}
library(flexdashboard)

library(tidyverse)
library(viridis)
library(p8105.datasets)

library(plotly)
```
```{r}
data(rest_inspec)

#tidy
rest_inspec_tidy=
  rest_inspec %>% 
  select(
    boro, zipcode, dba, cuisine_description, building, grade, score
  ) %>% 
  filter(
    !is.na(grade),
    grade %in% c("A", "B", "C", "Not Yet Graded"),
    cuisine_description == c("Korean", "Chinese", "American", "Donuts")
  ) %>% 
  mutate(
    grade=as.factor(grade),
    grade=fct_relevel(grade, c("A", "B", "C", "Not Yet Graded"))
  )
```
```

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}
rest_inspec_tidy %>% 
  filter(
    cuisine_description=="Chinese"
  ) %>% 
  plot_ly(x=~score, y=~zipcode, type="scatter", mode="markers", color=~boro, alpha=0.5 ) %>%
  layout(title="Scatter of Score by Zipcode by Borough ",
         xaxis= list(title="Score"), yaxis=list(title="Zipcode"))
```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}
rest_inspec_tidy%>% 
  filter(boro=="MANHATTAN") %>% 
  count(cuisine_description) %>% 
  mutate(cuisine_description = fct_reorder(cuisine_description, n)) %>% 
  plot_ly(x= ~cuisine_description, y= ~n, color = ~cuisine_description, type="bar") %>% layout(title="Number of Restaurants per Kelly's Favorite Food Categories in Manhattan ",
         xaxis= list(title="Cuisine Description"), yaxis=list(title="Count"))
```

### Chart C

```{r}
box_ggplot=
  rest_inspec_tidy%>% 
  mutate(grade = fct_reorder(grade, score)) %>% 
  plot_ly(x=~grade, y=~score, color=~cuisine_description, type = "box")%>% 
  layout(boxmode = "group") %>% 
  layout(title = "Distribution of Grade and Score per Cuisine Category in NYC", xaxis=list(title="Restaurant Grade"), yaxis=list(title="Score"))

ggplotly(box_ggplot)
```

