---
title: "Plotly Code and Explanation"
output: 
  html_document:
    cold_folding: hide
    toc: true
    toc_float: true
---

My name is Kelly and I am a second year Master of Public Health student at Columbia University's Mailman School of Public Health in the department of Biostatistics. I am learning to make websites with _interactive graphics_!!

## Heres some plots 
```{r}
library(tidyverse)
library(viridis)
library(p8105.datasets)

library(plotly)
```

```{r}
data(rest_inspec)

#tidy
rest_inspec_tidy=
  rest_inspec %>% 
  select(
    boro, zipcode, dba, cuisine_description, building, grade, score
  ) %>% 
  filter(
    !is.na(grade),
    grade %in% c("A", "B", "C", "Not Yet Graded"),
    cuisine_description == c("Korean", "Chinese", "American", "Donuts")
  ) %>% 
  mutate(
    grade=as.factor(grade),
    grade=fct_relevel(grade, c("A", "B", "C", "Not Yet Graded"))
  )
```
# Scatterplot 

I'm curious, how many Chinese Restaurants are in NYC and what is the distribution of scores  by zipcode stratified by borough?
```{r}
rest_inspec_tidy %>% 
  filter(
    cuisine_description=="Chinese"
  ) %>% 
  plot_ly(x=~score, y=~zipcode, type="scatter", mode="markers", color=~boro, alpha=0.5 ) %>%
  layout(title="Scatter of Score by Zipcode by Borough ",
         xaxis= list(title="Score"), yaxis=list(title="Zipcode"))

```
We can see here that based off of zipcode, it would make sense that the boroughs are clustered around the same zipcodes. What I personally find somewhat confusing is that the zipcodes for Brooklyn and Queens overlap--why not stay consistent like the other boroughs? It is interesting to see that Staten Island does not have a lot of Chinese restaurants with high scores. Brooklyn and Queens seem to have some high score restaurants along with Manhattan. However, I personally find the best tasting Chinese restaurants to be in Flushing, where the score may not be as high. 

## Bar Chart 
I was curious to see in Manhattan, how many restaurants are in my favorite food categories, which are the following: Donut, Korean, Chinese, and American. (I have an addiction to McFlurries and Tuna Melt Sandwiches). Based off of this bar chart I see this: 

```{r}
rest_inspec_tidy%>% 
  filter(boro=="MANHATTAN") %>% 
  count(cuisine_description) %>% 
  mutate(cuisine_description = fct_reorder(cuisine_description, n)) %>% 
  plot_ly(x= ~cuisine_description, y= ~n, color = ~cuisine_description, type="bar") %>% layout(title="Number of Restaurants per Kelly's Favorite Food Categories in Manhattan ",
         xaxis= list(title="Cuisine Description"), yaxis=list(title="Count"))
```
We can see here that among the 4 cuisine categories, American is the most popular in Manhattan. I wonder how many are diners? I guess we'll never know unless we do further investigation... (until next homework assignment).

# box plots
From here we can see that American restaurants tend to be of higher score when they have not been graded (as we can see form the outliers). The ones I find interesting is the donut category--especially the one that was in category C but with a low score. Shouldn't lower score correlate with higher grade? So what is with that restaurant? I suppose more yelp reviews need to be done. 
```{r}
box_ggplot=
  rest_inspec_tidy%>% 
  mutate(grade = fct_reorder(grade, score)) %>% 
  plot_ly(x=~grade, y=~score, color=~cuisine_description, type = "box")%>% 
  layout(boxmode = "group") %>% 
  layout(title = "Distribution of Grade and Score per Cuisine Category in NYC", xaxis=list(title="Restaurant Grade"), yaxis=list(title="Score"))

ggplotly(box_ggplot)
```

If interested, you can access all of these here on my [dashboard](dashboard.html)

